Safe Memory Regions for Big Data Processing

### 2016-10-21 paper/typeinference-proofs.tex
unification proof

\begin{proof}
Intuitively, the lemma says that every region variable will be unified with
some region constant (by the generated constraints).
%
Region variables are introduced at call-sites and represent the formal region parameters for the call.
Some correspond to region parameters of types of input parameters, and these will be bound by the
actual input parameter expressions. Other region variables correspond to region parameters of the
return type. These are determined by the actual return-expression in the called function/method.
It can be shown that these will be bound to one of ``input region parameters'', provided the called
function/method is typable (\ie, if $\satC$ is satisfiable).

@@

% This property follows from several aspects of $\FB$, e.g., it does not admit uninitialized variables.
Note that the region \C{R} where a new object is allocated (by the \C{new} construct) is indicated
by the user (as \C{new@R}). If the user does not specify this, it defaults to the allocation
context region. Thus, this aspect is handled by the frontend, and does not require or use
the constraint solver.
\qed
% This property follows from the constraint-generation rules.
% , and the type system uniquely determines the region parameters of every value
\end{proof}

>>>>

\begin{proof}
The lemma formalizes the intuition that every region variable will be ``unified'' with
some region constant (by the generated constraints).
%
Region variables are introduced at call-sites and represent the formal region parameters for the call.
Some correspond to region parameters of types of input parameters, and these will be bound by the
actual input parameter expressions. Other region variables correspond to region parameters of the
return type. These are determined by the actual return-expression in the called function/method.
It can be shown that these will be bound to one of ``input region parameters'', provided the called
function/method is typable (\ie, if $\satC$ is satisfiable).

@@

% This property follows from several aspects of $\FB$, e.g., it does not admit uninitialized variables.
Note that the region \C{R} where a new object is allocated (by the \C{new} construct) is indicated
by the user (as \C{new@R}). If the user does not specify this, it defaults to the allocation
context region. Thus, this aspect is handled by the frontend, and does not require or use
the constraint solver.

Formally, we can prove via induction that if $\exprok{\stdcontext}{e}{\tau}{C}$ then
every region variable in the result type $\tau$ will be bound to one of the ``live''
region constants (\ie, region constants in $\A$).
\qed

\end{proof}
